A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-14 methodology.tex
root level scopes in picture

We propose a novel representation. Similar to the naive approach, we define the columns of our dataset as the set of items $\mathtt{NT} \cup \mathtt{BCE}$ collected from Syn. However, to account for order-sensitivity, we introduce two additional steps. Firstly, we record the number of occurrences of items from $\mathtt{NT} \cup \mathtt{BCE}$ within each root-level scope (e.g. structs, functions, impl blocks, etc). This captures the varying occurrence counts resulting from different element orders in the program. Secondly, we incorporate a weighting scheme, designed semi-automatically, to prioritize non-terminals that we consider more salient for Rust bugs.

\paragraph{Example: computing fixed-sized vectors.} Figure~\ref{fig:essence} depicts the fixed-sized vectors, as described in this subsection, for the change from Figure~\ref{fig:extraction}. It also depicts the essence of change, to be described immediately below.

@@

    \caption{\label{fig:essence}Multiplying the number of occurrences of items observed in the tree by their respective weights results in the essence of change, visualized with a circle pack figure at bottom right.}
\end{figure}

>>>>

We propose a novel representation. Similar to the naive approach, we define the columns of our dataset as the set of items $\mathtt{NT} \cup \mathtt{BCE}$ collected from Syn. However, to account for order-sensitivity, we introduce two additional steps. Firstly, we record the number of occurrences of items from $\mathtt{NT} \cup \mathtt{BCE}$ within each distinct root-level scope (e.g. structs, functions, impl blocks, etc). This captures the varying occurrence counts resulting from different element orders in the program. Secondly, we incorporate a weighting scheme, designed semi-automatically, to prioritize non-terminals that we consider more salient for Rust bugs.

\paragraph{Example: computing fixed-sized vectors.} Figure~\ref{fig:essence} depicts the fixed-sized vectors, as described in this subsection, for the change from Figure~\ref{fig:extraction}. We have omitted scope information from this Figure for space reasons; the relevant scope is \verb+ItemFn+, indicating that these non-terminals occur within a function. It also depicts the essence of change, to be described immediately below.

@@

    \caption{\label{fig:essence}Multiplying the number of occurrences of items observed in the tree by their respective weights results in the essence of change, visualized with a circle pack figure at bottom right. Scope information (ItemFn) omitted from column headings for space purposes.}
\end{figure}
